---
title: "Custom evmodel"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(evsim)
library(dplyr)
library(lubridate)
library(ggplot2)
library(purrr)
```


## Simplifying our model

Read the EV model JSON file that you built from Arnhem data set:

```{r}

```


The `evmodel` object obtained with `evprof` contains all statistic parameters of the Gaussian Mixture Models for both connection and energy models. However, these GMM can be quite complex with a lot of clusters (mixtures). To check the complexity of the models and describe all parameters within the JSON file, use the function `get_evmodel_parameters`:

```{r full ev model parameters}

```

Now use the function `get_evmodel_summary` to simplify these parameters and see them in a natural scale instead of logarithmic, and a single Gaussian Model per user profile and time-cycle:

```{r simplified ev model}

```

Make a scatter plot (using ggplot2 package) of the connection GMM values with a color for every user profile. Do these points correspond to the centroids of the user profiles?

```{r connection GMM plot}

```



## Save model to Excel

The list format from function `get_evmodel_summary` is also useful to save the model in Excel, since it can be saved directly in an Excel workbook where every time-cycle will be a different worksheet. Do that using `writexl` package.

```{r save model to Excel}

```



## Designing a custom model

The Excel file created with the previous command can be used as a template to define our custom user profiles and parameters. Think about 3 different user profiles that could be identified in a use case in Japan:

* 
* 
*

After editing the file we can read it again using `purrr` iteration and `readxl` functions:

```{r, eval=F}
custom_model <- purrr::map(
  readxl::excel_sheets("ev_model_custom.xlsx") %>% purrr::set_names(),
  ~ readxl::read_excel("ev_model_custom.xlsx", sheet = .x)
)
```

Then, functions `get_connection_models_from_parameters` and `get_energy_models_from_parameters` can create the objects required as `connection_GMM` and `energy_GMM` in `evsim::get_ev_model` function.

```{r connection GMM}

```

```{r energy GMM}

```

Now create the EV model using function `evsim::get_ev_model`, setting properly the rest of parameters:

```{r get evmodel}

```



