---
title: "Time-series"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(evsim)
library(dplyr)
library(lubridate)
library(dygraphs)
library(purrr)
library(tidyr)
library(ggplot2)
```



## EV demand

We can calculate the estimated demand with function `get_demand()`. Get the time-series demand of the first 100 sessions from the simulated data set, by user profile and **hourly** resolution:

```{r get demand}

```


We can visualize the estimated demand in an HTML plot using the function `plot_ts`:

```{r plot, echo=TRUE, fig.width=9}
estimated_demand %>% 
  plot_ts(ylab = 'Power demand (kW)', fillGraph = T, stackedGraph = T)
```


### Time-resolution makes a difference

Now get the same time-series demand but with **quarterly** resolution:

```{r}

```


Answer the following questions:

* Which is the peak demand for every user profile and both time resolutions?
* Which is the total energy consumed for every user profile and both time resolutions?



## EV occupancy

Get the EV occupancy of the simulated sessions, by user profile:

```{r get occupancy}

```



## Multi-core processing

We can discover the number of physical CPUs in our computer with function `parallel::detectCores`:
```{r number of cores}
# n_cores <- 
```


Below, an example of calculating the demand from the first 10.000 California EV charging sessions with different number of cores:

```{r sessions, echo = T, eval = F}
cores_time <- tibble(
  cores = 1:n_cores,
  time = 0
)
for (mcc in cores_time$cores) {
  results <- system.time(
    evsim::california_ev_sessions %>%
       head(10000) %>%
       mutate(Profile = "All") %>%
       get_demand(by = "Profile", resolution = 60, mc.cores = mcc)
  )
  cores_time$time[mcc] <- as.numeric(results[3])
}
```

Make a column plot (using ggplot2) of the time spent for every number of cores used:

```{r processing time column plot}

```


Which is the optimal number of cores to use?









